Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-27 article.qmd
Remove plots in figure 1

```{python}
# | echo: false
import numpy as np
import seaborn
from poincare import Derivative, Variable, System, initial
from poincare import Simulator

def plot(model, figheight):
    ax = (
        Simulator(model)
        .solve(save_at=np.linspace(0, 5, 101))
        .plot(figsize=(2, figheight))
    )
    ax.legend(frameon=False)
    seaborn.despine(ax.figure)

@@

:::: {#fig-code layout-nrow=3 .column-body-outset}

@@

$$
\begin{align}
    \dot{x} &= -x
    \\\\
    x(0) &= 1
\end{align}
$$

```{python}
# | echo: false
plot(Decay, 1)

@@

$$
\begin{align}
    \ddot{x} = -x
    \\\\
    \begin{cases}
        x(0) &= 1 \\
        \dot{x}(0) &= 0
    \end{cases}
\end{align}
$$

```{python}
# | echo: false
plot(Oscillator, 1.5)

@@

$$
\begin{align}
    \begin{cases}
        \dot{x} = -x \\
        \dot{y} = -y
    \end{cases}
    \\\\
    \begin{cases}
        x(0) &= 1 \\
        y(0) &= 2
    \end{cases}
\end{align}
$$

```{python}
# | echo: false
plot(BigModel, 1.5)

First-order system of two exponential decays.
:::
::::

>>>>

```{python}
# | echo: false
from poincare import Derivative, System, Variable, initial

@@

:::: {#fig-code layout-nrow=3}

@@

$$
\dot{x} = -x
$$

$$
x(0) = 1
$$

@@

$$
\ddot{x} = -x
$$

$$
\begin{cases}
    x(0) &= 1 \\
    \dot{x}(0) &= 0
\end{cases}
$$

@@

$$
\begin{cases}
    \dot{x} = -x \\
    \dot{y} = -y
\end{cases}
$$

$$
\begin{cases}
    x(0) &= 1 \\
    y(0) &= 2
\end{cases}
$$

First-order system of two exponential decays.
:::

Code and corresponding mathematical expressions for different systems.
::::
